Crawler and Inverted Index in Java

### 2023-11-05 latexJava/paperJava.tex
Added sections to paper

@@

There are various ways in which this project could be improved.

>>>>

The biggest improvement is the new tokenization algorithm, which is orders of magnitude faster than the old methods used in the project.
Also given that it is implemented by hand, it is much more flexible and can be easily modified to suit the needs of the project.

@@

In the future, the new file datamart could be improved further to be faster using all sorts of different caching techniques to reduce the number of IO operations.
